babette: BEAUti 2, BEAST2 and Tracer for R

### 2018-04-23 article.tex
Split article, according to Methods in Ecology and Evolution guidelines
Mention package reviewers

\usepackage{listings}
\usepackage{hyperref}
\usepackage{todonotes}
\usepackage{verbatim}
\usepackage{tikz}
\usepackage{tkz-graph}
\usepackage{pgf}
\usepackage{bm}

\usetikzlibrary{arrows,automata}

@@

\usetikzlibrary{calc}
\usetikzlibrary{arrows.meta}

@@

Thanks to Yacine Ben Chehida and Paul van Els for supplying their 
BEAST2 use cases. Thanks again to Paul van Els for the sharing his FASTA files 
for use by this package. Thanks to Leonel Herrera-Alsina, Raphael Scherrer 
and Giovanni Laudanno for their comments on this package and article.
We would like to thank the Center for Information Technology of the University 
of Groningen for their support and for providing access to the Peregrine 
high performance computing cluster.

@@

RJCB created the package. 
RJCB wrote the first manuscript draft. 
All authors critically revised the text and gave approval for publication.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figures at the end
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \resizebox {0.8\columnwidth} {!} {
    \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=6cm, semithick]   
    \tikzstyle{every state}=[]
    \node[state] (A) [rectangle] {
      \includegraphics[width=0.2\textwidth]{alignment.png}
    };   
    \node[state] (AL) [above left=-0.25cm and -0.25cm of A, fill=white] {
      1
    };   
    \node[state] (B) [right of = A, rectangle] {
      \includegraphics[height=0.15\textheight]{BeautiSiteModel.png}
    };   
    \node[state] (BL) [above left=-0.25cm and -0.25cm of B, fill=white] {
      2
    };   
    \node[state] (E) [below of=A, rectangle] {
      \includegraphics[height=0.1\textheight]{file2.png}
    };   
    \node[state] (EL) [above left=-0.25cm and -0.25cm of E, fill=white] {
      3
    };   
    \node[state] (C) [right of = E, rectangle] {
      \includegraphics[width=0.3\textwidth]{beast_logo.png}
    };   
    \node[state] (CL) [above left=-0.25cm and -0.25cm of C, fill=white] {
      4
    };   
    \node[state] (F) [rectangle, below of=E] {
      \includegraphics[height=0.1\textheight]{file.png}
    };
    \node[state] (FL) [above left=-0.25cm and -0.25cm of F, fill=white] {
      5
    };   
    \node[state] (H) [rectangle, below of=F] {
      \includegraphics[width=0.3\textwidth]{DensiTreeExample2.jpg}
    };
    \node[state] (HL) [above left=-0.25cm and -0.25cm of H, fill=white] {
      6
    };   
    \node[state] (I) [rectangle, right of=H] {
      \includegraphics[width=0.6\textwidth]{tracer_example_output.png}
    };
    \node[state] (IL) [above left=-0.25cm and -0.25cm of I, fill=white] {
      7
    };   
    \path 
      (A) edge [anchor = west] node {} (E)
      (E) edge [anchor = west] node {} (F)
      (F) edge [anchor = west] node {} (H)
      (F) edge [anchor = west] node {} (I)
    ; 
    \path [-o,draw] (B) -- ($ (A) !.5! (E) $);
    \path [-o,draw] (C) -- ($ (E) !.5! (F) $);
    \end{tikzpicture}
  }
  \caption{
    Workflow using GUI tools. From an alignment (1) and BEAUti (2), 
    a BEAST2 configuration file (3) is created. BEAST2 (4) uses that file
    to infer a posterior, storing it in multiple files (5). These results
    are visualized using DensiTree (6) and Tracer (7). babette allows
    for the same workflow, all from an R function call.
  }
  \label{fig:workflow}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\end{document}
\grid
\grid
\grid
\grid

>>>>

\usepackage{listings}
\usepackage{hyperref}
\usepackage{todonotes}
\usepackage{verbatim}
\usepackage{pgf}
\usepackage{bm}

@@

@@

Thanks to Yacine Ben Chehida and Paul van Els for supplying their 
BEAST2 use cases. Thanks again to Paul van Els for the sharing his FASTA files 
for use by this package. Thanks to Leonel Herrera-Alsina, Raphael Scherrer 
and Giovanni Laudanno for their comments on this package and article.
Thanks to rOpenSci, and especially Noam Ross, Guangchuang Yu and 
David Winter for reviewing the package's source code.
We would like to thank the Center for Information Technology of the University 
of Groningen for their support and for providing access to the Peregrine 
high performance computing cluster.

@@

RJCB and RSE conceived the idea for the package. RJCB created and tested the package, and wrote the first draft of the manuscript. RSE contributed substantially to revisions.

@@

@@

\end{document}
\grid
\grid
\grid
\grid
\grid
\grid
